% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textwidth}{5in} % set width of text portion
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

\begin{document}

% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\large\bf Octav I. Dragoi}
% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
\moveleft.5\hoffset\centerline{Hiltenspergerstrasse 83}
\moveleft.5\hoffset\centerline{80796 M{\" u}nchen, Deutschland}
\moveleft.5\hoffset\centerline{+40 720 389 958}
\moveleft.5\hoffset\centerline{octav.dragoi@gmail.com}
% \moveleft.5\hoffset\centerline{Romanian Citizenship}
% \moveleft.5\hoffset\centerline{}

\begin{resume}
  \vspace{10pt}

  \section{EDUCATION}
  % \sl will be bold italic in New Century Schoolbook (or
  % any postscript font) and just slanted in
  %	Computer Modern (default) font
  {\sl Master of Science\/} \hfill 2018 - 2020 (exp.)\\
  \textbf{Technische Universit{\"a}t M{\"u}nchen, Munich, Germany} \\
  {\sl Program\/}: Data Engineering and Analytics. \\
  {\sl Grade\/}: 1.385. (1 to 5, 1 is best)
  \vspace{-6pt}

  {\sl Coursework\/}: Foundations of Data Engineering, Nonlinear Optimization: Advanced,
  Introduction to Deep Learning, Foundations of Data Analysis, Combinatorial Optimization.
  \vspace{-6pt}

  {\sl Project Work\/}: \textbf{TUM Data Innovation Lab}, in partnership with \textbf{CapitalBay}. \\
  A real estate group project focused on building a model for predicting future house prices and rents across cities in Germany.
  Final results are uploaded \href{https://www.di-lab.tum.de/en/past-projects/capital-bay-revolution-of-real-estate-valuation/}{at this link.}

  {\sl Bachelor of Arts\/} \hfill 2012 - 2016\\
  \textbf{Harvard College, Cambridge, MA} \\
  {\sl Concentration\/}: Mathematics and Computer Science. \\
  {\sl Secondary Field\/}: Economics. \\
  {\sl Overall GPA\/}: 3.75/4.00  \\
  {\sl GRE Scores\/}: 163 Verbal, 170 Quant.
  \vspace{-6pt}

  {\sl Coursework\/}:  Honors Abstract Algebra, Honors Real and Complex Analysis, Differential Topology,
    Analytic Number Theory, Algebraic Geometry; General Computer Science, Data Structures and
    Algorithms, Machine Learning, Data Science.
  \vspace{-6pt}

  {\sl Thesis\/}: \href{http://math.harvard.edu/theses/senior/dragoi/dragoi.pdf}
  {The Sarnak Conjecture. Orthogonality of the Mobius Function on Bounded Depth Circuits.} \\
  Explored a result from 2012 proving a particular case of the Sarnak conjecture that links
  concepts from analytic number theory with abstract computational theory.
  \vspace{-6pt}

  {\sl High School}\hfill 2008 - 2012 \\
  \textbf{International Computer Highschool of Bucharest, Romania}\\
  Valedictorian GPA 10/10.\\
  SAT Scores: 800 Math, 800 Writing, 750 Reading, 800 Math II, 800 Physics
  \vspace{8pt}

  \section{AWARDS} \textbf{Putnam Mathematical Competition}
  \begin{itemize} \itemsep -2pt
    \item 10\textsuperscript{th} in 2012, in the N1 niche of the national rankings.
    \item Honorable Mentions in 2013 and 2014.
  \end{itemize}
  \textbf{International Mathematical Olympiad}
  \begin{itemize} \itemsep -1pt
    \item Gold Medal in 2011, Amsterdam, the Netherlands.
    \item Silver Medal in 2012, Mar del Plata, Argentina.
  \end{itemize}
  \textbf{Balkan Mathematical Olympiad}
  \begin{itemize} \itemsep -1pt
    \item Gold Medal in 2010, Chisinau, Moldova.
    \item Gold Medal in 2011, Iasi, Romania.
    \item Gold Medal in 2012, Antalya, Turkey.
  \end{itemize}
  \newpage

  \section{EXPERIENCE}
  {\sl Algorithmic Trader} \hfill Summer 2016 - Fall 2018 \\
  \textbf{Jump Trading LLC, New York, NY} \\
  A quantitative, proprietary trading company and registered market maker.
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Part of a team of 8 people trading equities worldwide.
      Studying statistical properties of market data and implementing black-box
      trading algorithms.
    \item Created a framework that improves the entire team's performance by 20\%. Designed and
      researched several new trading strategies. Implemented several essential components and features
      for the trading platform.
    \item Working on the full process pipeline: feature design, data analysis,
      phenomenon modeling, algorithm implementation, production code maintenance
      and efficientization. All work done in a Linux environment.
    \item Besides the proprietary research framework, the toolkit includes Python and R
      for data analysis (\texttt{pandas}, \texttt{data.table}), machine learning (\texttt{xgboost})
      and distributed computation (\texttt{OpenMPI}), as well as C++ development tools
      (\texttt{valgrind}, \texttt{GDB}).
  \end{itemize}


  {\sl Quantitative Summer Analyst} \hfill Summer 2015 \\
  \textbf{D.E. Shaw \& Co., New York, NY} \\
  A large hedge fund, well known for employing quantitative strategies.
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Studied trend filtering methods and models
      that remove short-term noise and retain only the long-term significant movements.
      Developed new methods and compared them with already existing ones.
    \item Implemented a Python package of the aforementioned theoretical models
      and researched its practical predictive power on timeseries of market data.
  \end{itemize}

  {\sl Summer Analyst Intern} \hfill Summer 2014 \\
  \textbf{Ellington Management Group LLC, Old Greenwich, CT} \\
  A Connecticut-based hedge fund focused on trading mortgage-based securities.
  Worked in two separate departments, statistical arbitrage and research.
  \begin{itemize} \itemsep -2pt
    \item Focused on creating higher frequency stat-arb signals.
      Did statistical analysis and data mining on intraday order book data for index ETFs.
    \item Worked on an agent-based housing market model, meant to reproduce and explain the
      subprime mortgage crisis associated with the Great Recession.
  \end{itemize}

  \section{EXTRA-CURRICULAR \\ ACTIVITIES} Member of the Harvard Financial Analysts Club.
    \hfill Fall 2012 - Spring 2016 \\
  Regular Course Assistant of the Math Department. \hfill Fall 2013 - Spring 2016 \\
  Member of the Harvard $\Sigma$AE fraternity. \hfill Spring 2013 - Spring 2016 \\
  Faculty member of AwesomeMath Summer Camp. \hfill Summer 2012
  \begin{itemize} \itemsep -2pt
    \item Took place in Santa Cruz, CA. Held lectures for a class with 40 students,
      also designed tests and team contest problems. \\
  \end{itemize}

  \section{PUBLICATIONS} 
  Klischat, Moritz, Octav Dragoi, Mostafa Eissa and Matthias Althoff. \\
  “Coupling SUMO with a Motion Planning Framework for Automated Vehicles.” \\
  \textit{SUMO} (2019).

  \section{COMPUTER \\ \& LANGUAGE \\ SKILLS} {\sl Programming:\/} Python, C++, R, bash, \LaTeX  \\
  {\sl Languages:\/} Romanian (native), English (proficient), French, Russian, German (conversational).

\end{resume}
\end{document}
